--- 
title: "Exploratory Analysis Project"
author: "Matheus Amaral Mões, Marcelo Semerene Farah, Luísa Belus Henriques and Daniela de Góes N. Georg"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
biblio-style: apalike
description: "This project is part of a lesson from FGV's MBA on Business Analytics and Big Data."

---

#Introduction

This project is part of the Exploratory Data Analysis discipline in Fundação Getúlio Vargas’s Business Analytics and Big Data MBA. Members of the group: Matheus Amaral Mões, Marcelo Semerene Farah, Luísa Belus Henriques and Daniela de Góes Nogueira Georg.

Context and Objective

The manager of a Czech bank wants to get a better understanding on his clients. To do so, it has an extensive database that records customers and their transactions.

To assist the manager, our team worked with the database in the following steps:

1. Understand, clean and organize data;

2. Search relationships between data;

3. Find products and service opportunities for the bank.

This book is organized according to the steps taken to reach a conclusion about the clients.



```{r include = FALSE}
#install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')

pdf <- FALSE
```

